---
title: "Mi Band Data Analysis"
author: "Vinayak"
date: "7/3/2019"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float: yes
---
# Objective
* To understand the effect of transformation of variables on linear regression models  

## Simple Model
* Building a simple linear regression model in order to study the variation of y (Ahead of % people) w.r.t x (Streak i.e. continuous days of walk)
```{r warning = FALSE}
library(readxl)
setwd("C:\\Users\\nayak\\Desktop\\INSOFE\\CSE 7402C\\20190630_Batch64_CSE7402c_Multiple_Linear Regression_Lec02")
miBand_data = read_excel("Regression.xlsx", sheet = "MiBand2", col_names = TRUE)
miBand_data = miBand_data[,c(1,2)]
colnames(miBand_data) = c("Streak", "Ahead_of_percent_people")
head(miBand_data,5)
plot(miBand_data$Streak, miBand_data$Ahead_of_percent_people,
     xlab = "Streak", ylab = " Ahead of % People",
     main = "Ahead of % People vs Streak",
     cex.axis = 0.6, cey.axis = 0.6)
```

Fit a linear model Y = f(x).

```{r warning = FALSE}
test_data = miBand_data[74,]
head(test_data)
simple_model = lm(Ahead_of_percent_people~I(Streak^2), data = miBand_data)


print(paste("Adjusted R-Sq of the model",   
          sprintf("%.2f",summary(simple_model)$adj.r.squared)))
summary(simple_model)
par(mfrow = c(2,2))
plot(simple_model)

par(mfrow = c(1,1))
plot(miBand_data$Streak, miBand_data$Ahead_of_percent_people,
     xlab = "Streak", ylab = " Ahead of % People",
     main = "Ahead of % People vs Streak",
     cex.axis = 0.6, cey.axis = 0.6)
abline(simple_model)

miBand_data$SimpPred = predict(simple_model, newdata = miBand_data)
test_data$SimpPred = predict(simple_model, newdata = test_data)
test_data$Error = test_data$Ahead_of_percent_people - test_data$SimpPred
test_data
```

## Transforming x to logscale

Make a column log(Streak) and append it to the dataframe. Then fit a model to this data and make predictions accordingly.
```{r warning = FALSE}
miBand_data$logx = log(miBand_data$Streak, base = exp(1))
test_data = miBand_data[74,]
head(test_data)
log_model = lm(Ahead_of_percent_people~logx, data = miBand_data)
print(paste("Adjusted R-Sq of the model",   
          sprintf("%.2f",summary(log_model)$adj.r.squared)))
summary(log_model)
par(mfrow = c(2,2))
plot(log_model)
par(mfrow = c(1,1))
plot(miBand_data$logx, miBand_data$Ahead_of_percent_people,
     xlab = "Log(Streak)", ylab = " Ahead of % People",
     main = "Ahead of % People vs Log(Streak)",
     cex.axis = 0.6, cey.axis = 0.6)
abline(log_model)

miBand_data$LogPred = predict(log_model, newdata = miBand_data)
test_data$LogPred = predict(log_model, newdata = test_data)
test_data$LogErr = test_data$Ahead_of_percent_people - test_data$LogPred
test_data
```

## Making y quadratic 
* Using $Y^2$ as our dependent variable to calculate the errors.
```{r warning = FALSE}
miBand_data$ysq = miBand_data$Ahead_of_percent_people * miBand_data$Ahead_of_percent_people
test_data = miBand_data[74,]
head(test_data)
Sq_model = lm(ysq~Streak, data = miBand_data)
print(paste("Adjusted R-Sq of the model",   
          sprintf("%.2f",summary(Sq_model)$adj.r.squared)))
summary(Sq_model)
par(mfrow = c(2,2))
plot(Sq_model)
par(mfrow = c(1,1))
plot(miBand_data$Streak, miBand_data$ysq,
     xlab = "Streak", ylab = " Ahead of % People Squared",
     main = "Ahead of % People Squared vs Streak",
     cex.axis = 0.6, cey.axis = 0.6)
abline(Sq_model)

miBand_data$SqPred = sqrt(predict(Sq_model, newdata = miBand_data))
test_data$SqPred = sqrt(predict(Sq_model, newdata = test_data))
test_data$SqErr = test_data$Ahead_of_percent_people - test_data$SqPred
test_data
```
## Comparison of Errors
```{r message = FALSE}
library(DMwR)

miBand_data = miBand_data[complete.cases(miBand_data),]

print("Simple Model Statistics")
sprintf("%.2f",regr.eval(miBand_data$Ahead_of_percent_people, miBand_data$SimpPred))

print("Log Streak Model Statistics")
sprintf("%.2f",regr.eval(miBand_data$Ahead_of_percent_people, miBand_data$LogPred))

print("Squared Ahead of people Model Statistics")
sprintf("%.2f",regr.eval(miBand_data$Ahead_of_percent_people, miBand_data$SqPred))
```





